Placeholder title: Formal methods in constraint-based learning

### 2023-12-21 ITP draft/draft.tex
minor polishing

POSSIBLY AN ADDITIONAL PARAGRAPH ON NON-ML MATH FORMALISATION THAT IS TANGENTIALLY SIMILIAR.

@@

Different functions, lemmas, and things that peraphs stand out.

@@

Implementation of the semantics: 
\begin{itemize}
	\item $type\_translation$ semantics of types
	\item a word on translation of indices and vectors using tuples
	\item mention Real library from Mathcomp to handle reals
	\item $translation$ - a semantics for all fuzzy DLs. Here there needs to be explanation maybe of how DL2 and STL are separate from the fuzzy logics as they are different enough to warrant a separate definition and lemmas, not enough overlap
	translation itself is dependently typed, handles 4 different fuzzy logics through use of global variable (for now it's global variable, up for discussion)

>>>>

POSSIBLY AN ADDITIONAL PARAGRAPH ON NON-ML MATH FORMALISATION THAT IS TANGENTIALLY SIMILAR.

@@

Different functions, lemmas, and things that perhaps stand out.

@@

Implementation of the semantics: 
\begin{itemize}
	\item $type\_translation$ semantics of types
	\item a word on translation of indices and vectors using tuples
	\item mention Real library from MathComp to handle reals
	\item $translation$ - a semantics for all fuzzy DLs. Here there needs to be explanation maybe of how DL2 and STL are separate from the fuzzy logics as they are different enough to warrant a separate definition and lemmas, not enough overlap
	translation itself is dependently typed, handles 4 different fuzzy logics through use of global variable (for now it's global variable, up for discussion)
